### 2023-04-27 chapter2/chapter2.tex
Added comparative methods citation

Therefore, in this work we apply a series of phylogenetic models to a set of orthologous IDRs identified in the \textit{Drosophila} genome to dissect the forces driving their evolution. Our analyses span multiple levels, ranging from the sequences that compose these regions to the distributed features that characterize them as a whole. For the latter, though the previous approach relied on simulations to generate the null distribution for a hypothesis of no constraint, we instead leverage a fully statistical phylogenetic comparative framework. By comparing models of constrained and unconstrained continuous trait evolution, \textit{i.e.} the Brownian motion and Ornstein-Uhlenbeck models, respectively, we can demonstrate evidence of selective constraint on features independent of any assumptions about the underlying process of sequence evolution. However, we also explore hybrid approaches that combine simulations with phylogenetic comparative methods to test increasingly refined models of IDR evolution. We find that IDRs exhibit unique patterns of amino acid substitution and that in some proteins disorder itself is a dynamically evolving property. Furthermore, though IDRs are broadly unconstrained along several axes of feature evolution, we identify specific clusters of IDRs with shared patterns of feature constraint. As in yeast, these clusters are enriched for proteins with specific functional annotations, which suggests the preservation of distributed features and their associated functions is a widespread mechanism of IDR evolution.

>>>>

Therefore, in this work we apply a series of phylogenetic models to a set of orthologous IDRs identified in the \textit{Drosophila} genome to dissect the forces driving their evolution. Our analyses span multiple levels, ranging from the sequences that compose these regions to the distributed features that characterize them as a whole. For the latter, though the previous approach relied on simulations to generate the null distribution for a hypothesis of no constraint, we instead leverage a fully statistical phylogenetic comparative framework~\cite{Cornwell2017}. By comparing models of constrained and unconstrained continuous trait evolution, \textit{i.e.} the Brownian motion and Ornstein-Uhlenbeck models, respectively, we can demonstrate evidence of selective constraint on features independent of any assumptions about the underlying process of sequence evolution. However, we also explore hybrid approaches that combine simulations with phylogenetic comparative methods to test increasingly refined models of IDR evolution. We find that IDRs exhibit unique patterns of amino acid substitution and that in some proteins disorder itself is a dynamically evolving property. Furthermore, though IDRs are broadly unconstrained along several axes of feature evolution, we identify specific clusters of IDRs with shared patterns of feature constraint. As in yeast, these clusters are enriched for proteins with specific functional annotations, which suggests the preservation of distributed features and their associated functions is a widespread mechanism of IDR evolution.
